Deep Reinforcement Learning for Conservation Decisions

### 2021-06-11 manuscript/manuscript.Rmd
finally, an abstract

---
title: Deep Reinforcement Learning for Conservation Decisions
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Melissa Chapman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Kari Norman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
output: 
  rticles::arxiv_article:
    keep_tex: true
  word_document: default
editor_options: 
  markdown: 
    wrap: sentence
---

>>>>

---
title: Deep Reinforcement Learning for Conservation Decisions
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Melissa Chapman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Kari Norman
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu
abstract: |
  Can machine learning really help us make better decisions about a changing planet?
  In this paper, we illustrate and discuss the potential of a promising 
  corner of machine learning known as _reinforcement learning_ (RL) to help tackle the
  most challenging conservation decision problems. RL is uniquely
  well suited to conservation and global change challenges for three reasons: (1)
  rather than passively modeling observed data, RL is explicitly designed around 
  the actions of an agent who _interacts_ with an environment which is dynamic and uncertain,
  (2) RL approaches do not require massive amounts of data, (3) RL approaches would 
  utilize rather than replace existing models, simulations, and the knowledge they contain.
  We provide a conceptual and technical introduction to RL and its relevance to ecological
  and conservation challenges, including examples of both a previously solved problem in setting
  fisheries quotas and a previously unsolved problem in managing ecological tipping points.
  Four appendices with annotated code provide a tangible introduction to researchers 
  looking to adopt, evaluate, or extend these approaches.

keywords:
  - Reinforcement Learning
  - Conservation
  - Machine Learning
  - Artificial Intelligence
  - Tipping points
bibliography: references.bib
header-includes:
  - \usepackage{amsmath}
  - \usepackage{amssymb}
output: 
  rticles::arxiv_article:
    keep_tex: true
  word_document: default
editor_options: 
  markdown: 
    wrap: sentence
---
